Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-21 docs/questioning.tex
filled all tables.

        \multirow{12}{*}{Training}

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,0,0,0)\_a & {\bf ?} & {\sc sql} injection \\ 

@@

	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql} injection, {\sc xss} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5--24\% & {\sc xss} \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & \tick,\tick & 39\% & {\sc sql} and {\sc xp}ath injection \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql} and No{\sc sql} injection \\

@@

Notes on {\sc isr} mechanisms:
\begin{enumerate}
\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve}.
\item {\it Noncespaces}~\cite{GC09} was only tested on one
known vulnerable application (TikiWiki). The authors mention that they performed
a number of attacks but they do not state how many.
\item The authors of {\it x{\sc js}}~\cite{APKLM10}, have tested
their mechanisms based on real-world attacks coming from
{\sc xss}ed.com.\footnote{www.xssed.com}
\end{enumerate}

@@

Notes on training-based mechanisms:
\begin{enumerate}
\item {\it {\sc didafit}}~\cite{LLW02} is one of
the first {\sc ids}.
\item {\sc amnesia}~\cite{HO05,HO06,HO05b} was tested
on applications with known vulnerabilities taken
from \url{http://gotocode.com} plus two synthetic benchmarks.
Interestingly, in one of the papers~\cite{HO06},
the authors mention that the tool can produce both {\sc fp} and
{\sc fn}.
\item {\it libAnomaly}~\cite{VMV05} --- one application tested ({\sc php}-Nuke).
\item {\sc sqlg}uard~\cite{BWS05} --- no testing at all.
\end{enumerate}

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline    
	\multirow{12}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
    &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
	&   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
	\hline
    \end{tabular}}
        \begin{tablenotes}
	\begin{footnotesize}
       \item[1] The check mark (\tick) indicates that some point within
       the publication there is a homepage where the reader can refer to, to
       download the corresponding software. {\sc ao} (Available On-line) suggests
       that the software is available on-line but the
       address was not mentioned in the paper, which probably indicates that
       the authors made it available after the publication. The question ({\bf ?})
       mark, indicates that the a homepage for the software was included
       in the publication but now it is not available.
	\end{footnotesize}
    \end{tablenotes}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}

>>>>

        \multirow{11}{*}{Training}

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\bf ?} & {\sc sql} injection \\ 

@@

	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\bf ?} & {\sc sql} injection, {\sc xss} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\bf ?} &  {\sc xss} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
	& 	{\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\

@@

Notes on {\sc isr} mechanisms:
\begin{enumerate}
\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve} --- though
this is not mentioned in the publication.
\item {\it Noncespaces}~\cite{GC09} was only tested on one
known vulnerable application (TikiWiki). The authors mention that they performed
a number of attacks but they do not state how many.
\item The authors of {\it x{\sc js}}~\cite{APKLM10}, have tested
their mechanisms based on real-world attacks coming from
{\sc xss}ed.com.\footnote{www.xssed.com}
\end{enumerate}

@@

Notes on training-based mechanisms:
\begin{enumerate}
\item {\it {\sc didafit}}~\cite{LLW02} is one of
the first {\sc ids}.
\item {\sc amnesia}~\cite{HO05,HO06,HO05b} was tested
on applications with known vulnerabilities taken
from \url{http://gotocode.com} plus two synthetic benchmarks.
Interestingly, in one of the papers~\cite{HO06},
the authors mention that the tool can produce both {\sc fp} and
{\sc fn}.
\item {\it libAnomaly}~\cite{VMV05} --- one application tested ({\sc php}-Nuke).
\item {\sc sqlg}uard~\cite{BWS05} --- no testing at all.
\item {\sc sm}ask~\cite{JB07} was tested on real-world applications
with exploits from {\sc cve} --- though this is not mentioned in the publication.
\item {\sc xssds}~\cite{JEP08} --- testing was based on 
defects found in the security mailing
list: {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
The authors provide multiple {\sc fp} rates depending on the experiment.
\item {\sc xss-guard}~\cite{BV08} was tested on real-world applications
with exploits from {\sc cve}.
\item {\sc swap}~\cite{WPLKK09} was tested on a real-world application ({\sc phpbb})
with exploits from {\sc cve} --- though this is not mentioned in the publication.
%\item {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} have developed a
%mechanism to detect {\sc sql} and {\sc xp}ath injection attacks
%only on web services. Their testing involve a real-world benchmark
%({\sc tpc}-app).\footnote{\url{http://www.tpc.org/}}
\item {\it Diglossia}~\cite{SMS13} was tested on real-world applications
with exploits from {\sc cve}.
\end{enumerate}

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline    
	\multirow{12}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
    &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
	&   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline  
        \multirow{11}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
    \end{tabular}}
        \begin{tablenotes}
	\begin{footnotesize}
       \item[1] The check mark (\tick) indicates that some point within
       the publication there is a homepage where the reader can refer to, to
       download the corresponding software. {\sc ao} (Available On-line) suggests
       that the software is available on-line but the
       address was not mentioned in the paper, which probably indicates that
       the authors made it available after the publication. The question ({\bf ?})
       mark, indicates that the a homepage for the software was included
       in the publication but now it is not available.
	\end{footnotesize}
    \end{tablenotes}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}
